Composition-climate paper

### 2015-04-11 Composition_Ecology.Rmd
* Minor changes to the Methods text. * Moved a bunch of new files in. * I've changed how I'm generating climate, and switched to a PRISM dataset on my local hard-drive.  To do this I've had to write `r/building_small_climate.R`, it's the raw code that generates the subset data. * The above change has meant large changes to `R/load_climate.R` which is now considerably simpler.

The analysis follows a blocked sampling method.  We generate probability density functions for actual PLSS presence, by taxon, at the settlement era and for the same PLSS space in the modern era.  We also generate climate data for the FIA presence, and we generate climate space for modern land use.  In this way we can test how much of the change in shape is the result of changing land use vs changing climate since the early part of the century.

@@

Results
---------------

>>>>

The analysis follows a blocked sampling method.  We generate probability density functions for actual PLSS presence, by taxon, at the settlement era and for the same PLS taxa (and point locations) in the modern era.  We also generate climate data for the FIA presence, and we generate climate space for modern land use.  In this way we can test how much of the change in shape is the result of changing land use vs changing climate since the early part of the century.

@@

Results
---------------
Across the region PLS cells account for X
